Bird beak's elaboration and exploration

### 2021-09-24 Analysis/02-MCMCglmm_mini_chains.Rmd
added mini chains figure

@@

```{r, parametrise_the_model, eval = FALSE}
## Set up the parametrising chains models on the demo data
param_MCMCglmm <- make.mini.chains(data         = traitspace,
                                   dimensions   = 1:3,
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "clade"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 20000,
                                       thin   = 500,
                                       burnin = 0))

>>>>

![mini chain diagram](../Manuscript/Figures/mini-chains_diagram.png "Mini chains diagram")

@@

```{r, parametrise_the_model, eval = FALSE}
## Set up the parametrising chains models on the demo data
param_MCMCglmm <- make.mini.chains(data         = traitspace,
                                   dimensions   = 1:3,
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "clade"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 50000,
                                       thin   = 500,
                                       burnin = 0))
